---
title: "PORT: interpretation biases variance"
author: "Thomas McGregor"
date: "`r Sys.Date()`"
output: html_document
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../reports"
    )
  })
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load packages, include=FALSE}
# Clear workspace
rm(list = ls())

# Load packages
library(broom) # tidying output
library(corrr) # creating correlation matrices & heatmaps
library(gt) # creating tables
library(gtsummary) # creating tables
library(here) # file referencing
library(naniar) # visualise missing data
library(ppcor) # partial correlations
library(summarytools) # data exploration
library(tidyverse) # data manipulation
library(webshot) # required for saving gt tables
```

```{r read in dataset, include=FALSE}
port_data <- read_rds(here("data", "processed", "merged", "07_imputed-processed-data.Rds"))
```

# Cleaning

## Subsets

```{r create subsets}
# Exclusions applied: all variables, filtered participants
port_data_exclusions_applied <- port_data %>% 
  filter(port_exclusion == FALSE)

# Subsetted: selected variables
port_data_subsetted <- port_data %>% 
  select(
    participant_id,
    port_exclusion,
    
    gad7_screening_total,
    gad7_baseline_total,
    gad7_treatment_total_final,
    gad7_followup_total,
    
    phq9_screening_total,
    phq9_baseline_total,
    phq9_treatment_total_final,
    phq9_followup_total,
    
    wsas_screening_total,
    wsas_baseline_total,
    wsas_treatment_total_final,
    wsas_followup_total,
    
    stai_baseline_trait_total,
    fss_baseline_total,
    pmh_baseline_mean,
    pswq_baseline_total,
    asi_baseline_total,
    cbas_baseline_behavioural_social,
    cbas_baseline_behavioural_nonsocial,
    cbas_baseline_cognitive_social,
    cbas_baseline_cognitive_nonsocial,
    eacs_midapp_total,
    ius12_midapp_total,
    bas_midapp_drive,
    bas_midapp_fun_seeking,
    bas_midapp_reward_responsiveness,
    bis_midapp_total,
    epq_r_midapp_nscale
  )
    

# Subsetted, complete cases: selected variables, filtered participants, no missing data
port_data_subsetted_complete_cases <- na.omit(port_data_subsetted)
```

# Brief

Colette and I are just discussing the design of the study in the new grant and mulling on the **impact of selecting participants with GAD7 \>=8 for variance in worry, interpretation biases etc**.

In order to get a sense of this I wondered if one of you could **pull out means and SDs for worry, anxiety sensitivity, EACS, CBAS and SST (if it has been coded/cleaned)** so we can see how much variance there is in this type of selected sample. It would also be useful to see the **correlations between all of these variables and GAD7 scores** so we can see if the reduced variance has any impact on associations we'd expect to see.

## List of measures

-   GAD 7

-   PHQ9

-   WSAS

-   STAI-T

-   FSS

-   PMH-Scale

-   PSWQ

-   ASI

-   CBAS

-   EACS

-   IUS-12

-   BIS/BAS

-   EPQ-R Nscale

## Notes

-   SST is not clean and therefore not available for analyses

# GAD-7 scores over time

Graphic illustrating that over time (screening to baseline) and after treatment
a greater number of participants fell below the IAPT GAD-7 cut-off for anxiety
(>= 8).

Also, from a quick look, at screening there seems to be a few more participants
that were eventually excluded that fell below 8 on the GAD-7. However, it's only
around 20 participants, so I will keep them in.

I will produce descriptives and run correlations on the baseline timepoint as it
is closest to the measurement of interpretation biases. But it is worth noting 
that not all participants are 8 and above by this point.

```{r gad score plot, warning=FALSE}
port_data_subsetted %>% 
  select(participant_id, contains("gad7"), port_exclusion) %>% 
  pivot_longer(contains("gad7"), names_to = "variable", values_to = "score") %>%
  mutate(variable = factor(variable, levels = c("gad7_screening_total", "gad7_baseline_total", "gad7_treatment_total_final", "gad7_followup_total"))) %>% 
  ggplot(aes(x = variable, y = score, colour = port_exclusion)) +
  geom_point(alpha = 0.4, position = "jitter") +
  geom_hline(yintercept = 8, color = "red") +
  stat_summary(
    geom = "point",
    fun = "mean",
    size = 5,
    shape = 4
  )
```

# Means and standard deviations

```{r}
port_data_subsetted %>% 
  select(contains("baseline"), contains("midapp")) %>% 
  summarise(
    across(
    .cols = everything(),
    .fns = list(
      mean = ~ mean(.x, na.rm = TRUE),
      sd = ~ sd(.x, na.rm = TRUE),
      n = ~ sum(!is.na(.x))
    ),
    .names = "{.col}_{.fn}")) %>% 
  pivot_longer(everything()) %>% 
  separate_wider_regex(name, c(Measure = ".*", "_", var2 = ".*")) %>% 
  pivot_wider(names_from = var2, values_from = value) %>% 
  rename(Mean = mean, SD = sd) %>% 
  mutate(Measure = str_replace_all(str_remove(Measure, "_baseline|_midapp"), "_", " ")) %>% 
  mutate(across(.cols = c(Mean, SD), .fns = ~round(., 2))) %>% 
  gt()
```

# Correlations

```{r}
port_data_subsetted %>% 
  select(contains("baseline"), contains("midapp")) %>% 
  correlate() %>%
  autoplot(triangular = "lower") +
  geom_text(aes(label=round(r, digits=2)), size=2)

ggsave(here("reports", "figures", "baseline-biases-heat-map.pdf"), width = 45, height = 35, units = "cm")
```

