---
title: "PORT analyses"
author: "Thomas McGregor"
date: "`r Sys.Date()`"
output: html_document
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../reports"
    )
  })
---

```{r setup, include=FALSE}
# Default to preventing code, but not the results from appearing in the finished 
# file
knitr::opts_chunk$set(echo = FALSE)
```

```{r load packages, include=FALSE}
# Clear workspace
rm(list = ls())

# Load packages
library(broom) # tidying output
library(gt) # creating tables
library(here) # file referencing
library(naniar) # visualise missing data
library(ppcor) # partial correlations
library(summarytools) # data exploration
library(tidyverse) # data manipulation
library(webshot) # required for saving gt tables
```

```{r read data, include=FALSE}
# Read in master dataset
port_data <- read_rds(here("data", "processed", "merged", "07_imputed-processed-data.Rds"))
```

```{r subset}
# Create subsets

# Exclusions applied: all variables, exclusions applied
port_data_exclusions_applied <- port_data %>% 
  filter(port_exclusion == FALSE)

# Subsetted: selected variables, exclusions applied
port_data_subsetted <- port_data %>% 
  filter(port_exclusion == FALSE) %>% 
  select(
    ieso_treatment_completed_total,
    demographics_age_at_screening_years,
    demographics_biological_sex,
    gad7_treatment_total_1,
    gad7_treatment_total_final,
    gad7_treatment_total_final_observed,
    gad7_followup_total,
    exp_acquisition_cs_minus_mean,
    exp_extinction_cs_plus_mean,
    fss_baseline_total,
    fss_followup_total)

# Subsetted, complete cases: selected variables, exclusions applied, no missing 
# data
port_data_subsetted_complete_cases <- na.omit(port_data_subsetted)
```

```{r standardising}
# Standardise (z-score) all continuous variables included in analyses
port_data_exclusions_applied_std <- 
  port_data_exclusions_applied %>%
  mutate(across(
    .cols = c(
      exp_acquisition_cs_minus_mean,
      exp_extinction_cs_plus_mean,
      gad7_treatment_total_1,
      ieso_treatment_completed_total,
      demographics_age_at_screening_years,
      fss_baseline_total,
      exp_acquisition_differential_mean,
      exp_extinction_differential_mean,
      aff_break_cs_plus_mean,
      aff_break_cs_minus_mean,
      aff_post_cs_plus_mean,
      aff_post_cs_minus_mean,
      cbas_baseline_total,
      eacs_midapp_total,
      asi_baseline_total,
      phq9_treatment_total_1
    ),
    .fns = ~ c(scale(.x, scale = TRUE, center = TRUE)),
    .names = "{col}_z"
  ))
```

# Explore {.tabset}

## Visualise missing data

-   Should not be any missing data for variables derived from GLAD (i.e. age at screening & biological sex)
-   Same goes for fear conditioning variables as missing data should be imputed (i.e. acquisition CS- and extinction CS+)

```{r visualise missing data, warning=FALSE}
port_data_subsetted %>%  
vis_miss()
```

## Skew & kurtosis

Skewness and Kurtosis values all range between +/- 1.

```{r describe data}
port_data_subsetted %>% 
  # Remove non-numerical variables to avoid warnings
  select(-demographics_biological_sex) %>% 
  descr()
```

## Correlations

### Acquisition CS- x GAD-7 at last session {.tabset}

#### Partial correlation

```{r acq correlation gad7}
# Partial correlation
partial_correlation <- pcor.test(
  port_data_subsetted_complete_cases$gad7_treatment_total_final_observed,
  port_data_subsetted_complete_cases$exp_acquisition_cs_minus_mean,
  port_data_subsetted_complete_cases$gad7_treatment_total_1,
  method="pearson"
)

print(partial_correlation)
```

#### Scatterplot

```{r acq scatterplot gad7}
# Scatterplot
port_data_subsetted %>% 
  ggplot(aes(x = exp_acquisition_cs_minus_mean, y = gad7_treatment_total_final_observed)) +
  geom_point() + 
  geom_smooth(formula = y ~ x, method = "lm")
```

### Extinction CS+ x GAD-7 at last session {.tabset}

#### Partial correlation

```{r ext correlation gad7}
# Partial correlation
pcor.test(
  port_data_subsetted_complete_cases$gad7_treatment_total_final_observed,
  port_data_subsetted_complete_cases$exp_extinction_cs_plus_mean,
  port_data_subsetted_complete_cases$gad7_treatment_total_1,
  method="pearson"
)
```

#### Scatterplot

```{r ext scatterplot gad7}
# Scatterplot
port_data_subsetted %>% 
  ggplot(aes(x = exp_extinction_cs_plus_mean, y = gad7_treatment_total_final_observed)) +
  geom_point() + 
  geom_smooth(formula = y ~ x, method = "lm")
```

# Analyses {.tabset}

## Primary

### GAD-7 at last session {.tabset}

Primary analyses use fear conditioning expectancy ratings to predict last session GAD-7 scores while controlling for first session GAD-7 score and number of treatment sessions completed.

#### Acquisition CS-

```{r primary acq}
# Generate model
pri_acq_minus_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_acquisition_cs_minus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(pri_acq_minus_model)

# Save single row summary of model
pri_acq_minus_model_glance <- 
  glance(pri_acq_minus_model)

# Save summary dataframe of test results
pri_acq_minus_model_tidy <- 
  tidy(pri_acq_minus_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "primary", 
         model = "acquisition_cs_minus", 
         .before = everything())
```

#### Extinction CS+

```{r primary ext}
# Generate model
pri_ext_plus_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_extinction_cs_plus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(pri_ext_plus_model)

# Save single row summary of model
pri_ext_plus_model_glance <- 
  glance(pri_ext_plus_model)

# Save summary dataframe of test results
pri_ext_plus_model_tidy <- 
  tidy(pri_ext_plus_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "primary", 
         model = "extinction_cs_plus", 
         .before = everything())
```

#### Plot

```{r primary combine dataframes}
# Combine tidied dataframes for potential plotting and tables
primary_models_tidy <-
  rbind(pri_acq_minus_model_tidy, pri_ext_plus_model_tidy) %>%
  mutate(
    sig_05 = if_else(p.value <= 0.05, TRUE, FALSE),
    sig_05_adj = if_else(pval.adj <= 0.05, TRUE, FALSE),
    term = factor(if_else(str_detect(term, "exp_"), "fc", term)),
    iv = case_when(
      term == "gad7_treatment_total_1_z" ~ FALSE,
      term == "ieso_treatment_completed_total_z" ~ FALSE,
      TRUE ~ TRUE
    ),
    term = fct_rev(term)
  )
```

```{r plot function}
forest_plot <-
  function(data,
           x,
           y,
           group,
           colour,
           alpha,
           point_shape,
           error_low,
           error_high,
           bar_dodge,
           x_axis_low,
           x_axis_high,
           x_axis_break,
           predictor_label_1 = "Acquisition CS-",
           predictor_label_2 = "Extinction CS+",
           predictor_label_3 = is.null,
           predictor_label_4 = is.null) {
    
    # Initialise plot
    ggplot(data, 
           aes(x = {{x}},
               y = {{y}},
               group = fct_rev({{group}}),
               colour = {{colour}},
               alpha = {{alpha}})) +
      
      # Scatterplot layer
      geom_point(aes(shape = {{point_shape}}),
                 size = 2,
                 position = position_dodge(width = bar_dodge)) +
      
      # Error bars
      geom_errorbar(aes(xmin = {{error_low}}, 
                        xmax = {{error_high}}),
                    position = position_dodge(width = bar_dodge),
                    width = 0) +
      
      # X-axis
      scale_x_continuous(
        limits = c(x_axis_low, x_axis_high), 
        breaks = round(seq(x_axis_low, x_axis_high, by = x_axis_break), 1)) +
      
      # Line at zero
      geom_vline(xintercept = 0, linetype = "dashed") +
      
      # Colour/shape settings
      scale_color_manual(
        values = c("#811D1C", "#153860", "#FF4E00", "#55C1FF"),
        labels = c(predictor_label_1, predictor_label_2, predictor_label_3, predictor_label_4)
      ) +
      
      scale_shape_manual(values = c(1, 16),
                         labels = c("p > 0.05", "p <= 0.05")) +
      
      scale_alpha_discrete(range = c(0.5, 1),
                           labels = c("Covariate", "Explanatory")) +
      
      # Theme
      theme_minimal() +
      theme(
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        strip.text.x = element_blank(),
        plot.caption = element_text(hjust = 0),
        plot.title = element_text(size = 11),
        plot.subtitle = element_text(size = 10),
        legend.title = element_text(size = 9),
        legend.text = element_text(size = 8)
      ) +
      
      # Labels
      labs(
        x = "Standardised beta coefficients",
        y = element_blank(),
        shape = "Significance",
        color = "Model",
        alpha = "Variable type"
      )
  }
```

```{r primary plot, warning=FALSE}
primary_models_tidy %>%
  filter(term != "(Intercept)") %>%
  
  # Plot
  forest_plot(data = .,
           x = estimate,
           y = term,
           group = model,
           colour = model,
           alpha = iv,
           point_shape = sig_05_adj,
           error_low = conf.low,
           error_high = conf.high,
           bar_dodge = 0.2,
           x_axis_low = -5, 
           x_axis_high = 5,
           x_axis_break = 1) +
  
  # Labels
  scale_y_discrete(
    labels = c(
      "ieso_treatment_completed_total_z" = "Number of treatment sessions",
      "gad7_treatment_total_1_z" = "First session GAD-7 score",
      "fc" = "Fear conditioning predictor"
    )
  ) + 
  labs(
    caption = paste0("Intercepts",
      "\nModel 1 = ",
      round(pri_acq_minus_model$coefficients[1], digits = 2),
      "\nModel 2 = ",
      round(pri_ext_plus_model$coefficients[1], digits = 2)
    ))

suppressMessages(ggsave(here("reports", "figures", "primary-regression-forest-plot.png"),
       bg = "white"))
```

## Secondary

### Age/Sex adjustment {.tabset}

The first set of secondary analyses repeats the same models as the primary analyses, except age and sex are controlled for (included as covariates).

#### Acquisition CS-

```{r secondary age/sex acq}
# Generate model
sec_acq_minus_model1 <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_acquisition_cs_minus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z +
      demographics_age_at_screening_years_z +
      demographics_biological_sex,
    data = .
  )

# Model output
summary(sec_acq_minus_model1)

# Save single row summary of model
sec_acq_minus_model_glance1 <- 
  glance(sec_acq_minus_model1)

# Save summary dataframe of test results
sec_acq_minus_model_tidy1 <- 
  tidy(sec_acq_minus_model1, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 6)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "secondary - age and sex adjustment", 
         model = "acquisition_cs_minus", 
         .before = everything())
```

#### Extinction CS+

```{r secondary age/sex ext}
# Generate model
sec_ext_plus_model1 <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_extinction_cs_plus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z +
      demographics_age_at_screening_years_z +
      demographics_biological_sex,
    data = .
  )

# Model output
summary(sec_ext_plus_model1)

# Save single row summary of model
sec_ext_plus_model_glance1 <- 
  glance(sec_ext_plus_model1)

# Save summary dataframe of test results
sec_ext_plus_model_tidy1 <- 
  tidy(sec_ext_plus_model1, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 6)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "secondary - age and sex adjustment", 
         model = "extinction_cs_plus", 
         .before = everything())
```

#### Plot

```{r secondary age/sex combine dataframes}
# Combine tidied dataframes for potential plotting and tables
secondary_models_tidy1 <-
  rbind(sec_acq_minus_model_tidy1, sec_ext_plus_model_tidy1) %>%
  mutate(
    sig_05 = if_else(p.value <= 0.05, TRUE, FALSE),
    sig_05_adj = if_else(pval.adj <= 0.05, TRUE, FALSE),
    term = factor(if_else(str_detect(term, "exp_"), "fc", term)),
    iv = case_when(
      term == "gad7_treatment_total_1_z" ~ FALSE,
      term == "ieso_treatment_completed_total_z" ~ FALSE,
      term == "demographics_age_at_screening_years_z" ~ FALSE,
      term == "demographics_biological_sexmale" ~ FALSE,
      TRUE ~ TRUE
    ),
    term = factor(
      term,
      level = c(
        "(Intercept)",
        "demographics_biological_sexmale",
        "demographics_age_at_screening_years_z",
        "ieso_treatment_completed_total_z",
        "gad7_treatment_total_1_z",
        "fc"
      )
    )
  )
```

```{r secondary age/sex plot, warning=FALSE}
secondary_models_tidy1 %>%
  filter(term != "(Intercept)") %>%
  
  # Plot
  forest_plot(data = .,
           x = estimate,
           y = term,
           group = model,
           colour = model,
           alpha = iv,
           point_shape = sig_05_adj,
           error_low = conf.low,
           error_high = conf.high,
           bar_dodge = 0.3,
           x_axis_low = -5, 
           x_axis_high = 5,
           x_axis_break = 1) +
  
  # Labels
  scale_y_discrete(
    labels = c(
      "demographics_age_at_screening_years_z" = "Age",
      "demographics_biological_sexmale" = "Biological sex (male)",
      "ieso_treatment_completed_total_z" = "Number of treatment sessions",
      "gad7_treatment_total_1_z" = "First session GAD-7 score",
      "fc" = "Fear conditioning predictor"
    )
  ) +
  labs(
    caption = paste0("Intercepts",
      "\nModel 1 = ",
      round(sec_acq_minus_model1$coefficients[1], digits = 2),
      "\nModel 2 = ",
      round(sec_ext_plus_model1$coefficients[1], digits = 2)
    )
  )

suppressMessages(ggsave(here("reports", "figures", "secondary1-regression-forest-plot.png"),
  bg = "white"))
```

### GAD-7 at follow-up (DV) {.tabset}

The second set of secondary analyses repeats the same models as the primary analyses, except GAD-7 scores from follow-up are used as the outcome variable instead of GAD-7 scores from participants' final treatment session.

#### Acquisition CS-

```{r secondary followup gad acq}
# Generate model
sec_acq_minus_model2 <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_followup_total ~ 
      exp_acquisition_cs_minus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(sec_acq_minus_model2)

# Save single row summary of model
sec_acq_minus_model_glance2 <- 
  glance(sec_acq_minus_model2)

# Save summary dataframe of test results
sec_acq_minus_model_tidy2 <- 
  tidy(sec_acq_minus_model2, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "secondary - gad7 followup dv", 
         model = "acquisition_cs_minus", 
         .before = everything())
```

#### Extinction CS+

```{r secondary followup gad ext}
# Generate model
sec_ext_plus_model2 <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_followup_total ~ 
      exp_extinction_cs_plus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(sec_ext_plus_model2)

# Save single row summary of model
sec_ext_plus_model_glance2 <- 
  glance(sec_ext_plus_model2)

# Save summary dataframe of test results
sec_ext_plus_model_tidy2 <- 
  tidy(sec_ext_plus_model2, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "secondary - gad7 followup dv", 
         model = "extinction_cs_plus", 
         .before = everything())
```

#### Plot

```{r secondary followup gad combine dataframes}
secondary_models_tidy2 <- rbind(sec_acq_minus_model_tidy2, sec_ext_plus_model_tidy2) %>% 
  mutate(sig_05 = if_else(p.value <= 0.05, TRUE, FALSE),
         sig_05_adj = if_else(pval.adj <= 0.05, TRUE, FALSE),
         term = factor(if_else(str_detect(term, "exp_"), "fc", term)),
         iv = case_when(
           term == "gad7_treatment_total_1_z" ~ FALSE,
           term == "ieso_treatment_completed_total_z" ~ FALSE,
           TRUE ~ TRUE),
         term = fct_rev(term))
```

```{r secondary followup gad plot, warning=FALSE}
secondary_models_tidy2 %>%
  filter(term != "(Intercept)") %>%
  
  # Plot
    forest_plot(data = .,
           x = estimate,
           y = term,
           group = model,
           colour = model,
           alpha = iv,
           point_shape = sig_05_adj,
           error_low = conf.low,
           error_high = conf.high,
           bar_dodge = 0.2,
           x_axis_low = -5, 
           x_axis_high = 5,
           x_axis_break = 1) +
  
  # Labels
  scale_y_discrete(
    labels = c(
      "ieso_treatment_completed_total_z" = "Number of treatment sessions",
      "gad7_treatment_total_1_z" = "First session GAD-7 score",
      "fc" = "Fear conditioning predictor"
    )
  ) +
  labs(
    caption = paste0("Intercepts",
      "\nModel 1 = ",
      round(sec_acq_minus_model2$coefficients[1], digits = 2),
      "\nModel 2 = ",
      round(sec_ext_plus_model2$coefficients[1], digits = 2)
    )
  )

suppressMessages(ggsave(here("reports", "figures", "secondary2-regression-forest-plot.png"),
  bg = "white"))
```

### FSS scores at follow-up {.tabset}

The third set of secondary analyses repeats the same models as the primary analyses, except FSS scores from follow-up are used as the outcome variable instead of GAD-7 scores from participants' final treatment session and FSS scores at baseline are controlled for instead of first treatment session GAD-7 scores.

#### Acquisition CS-

```{r secondary fss acq}
# Generate model
sec_acq_minus_model3 <- 
  port_data_exclusions_applied_std %>%
  lm(
    fss_followup_total ~ 
      exp_acquisition_cs_minus_mean_z + 
      fss_baseline_total_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(sec_acq_minus_model3)

# Save single row summary of model
sec_acq_minus_model_glance3 <- 
  glance(sec_acq_minus_model3)

# Save summary dataframe of test results
sec_acq_minus_model_tidy3 <- 
  tidy(sec_acq_minus_model3, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "secondary - fss followup dv", 
         model = "acquisition_cs_minus", 
         .before = everything())
```

#### Extinction CS+

```{r secondary fss ext}
# Generate model
sec_ext_plus_model3 <- 
  port_data_exclusions_applied_std %>%
  lm(
    fss_followup_total ~ 
      exp_extinction_cs_plus_mean_z + 
      fss_baseline_total_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(sec_ext_plus_model3)

# Save single row summary of model
sec_ext_plus_model_glance3 <- 
  glance(sec_ext_plus_model3)

# Save summary dataframe of test results
sec_ext_plus_model_tidy3 <- 
  tidy(sec_ext_plus_model3, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "secondary - fss followup dv", 
         model = "extinction_cs_plus", 
         .before = everything())
```

#### Plot

```{r secondary fss combine dataframes}
secondary_models_tidy3 <- rbind(sec_acq_minus_model_tidy3, sec_ext_plus_model_tidy3) %>% 
  mutate(sig_05 = if_else(p.value <= 0.05, TRUE, FALSE),
         sig_05_adj = if_else(pval.adj <= 0.05, TRUE, FALSE),
         term = factor(if_else(str_detect(term, "exp_"), "fc", term)),
         iv = case_when(
           term == "fss_baseline_total_z" ~ FALSE,
           term == "ieso_treatment_completed_total_z" ~ FALSE,
           TRUE ~ TRUE),
         term = fct_rev(term))
```

```{r secondary fss plot, warning=FALSE}
secondary_models_tidy3 %>%
  filter(term != "(Intercept)") %>%
  
  # Plot
  forest_plot(data = .,
           x = estimate,
           y = term,
           group = model,
           colour = model,
           alpha = iv,
           point_shape = sig_05_adj,
           error_low = conf.low,
           error_high = conf.high,
           bar_dodge = 0.2,
           x_axis_low = -25, 
           x_axis_high = 25,
           x_axis_break = 5) +
  
  # Labels
  scale_y_discrete(
    labels = c(
      "ieso_treatment_completed_total_z" = "Number of treatment sessions",
      "fss_baseline_total_z" = "Pre-treatment FSS score",
      "fc" = "Fear conditioning predictor"
    )
  ) +
  labs(
    caption = paste0("Intercepts",
      "\nModel 1 = ",
      round(sec_acq_minus_model2$coefficients[1], digits = 2),
      "\nModel 2 = ",
      round(sec_ext_plus_model2$coefficients[1], digits = 2)
    ))

suppressMessages(ggsave(here("reports", "figures", "secondary3-regression-forest-plot.png"),
  bg = "white"))
```

## Exploratory {.tabset}

### Discrimination scores (IV) {.tabset}

The first set of exploratory analyses use US-expectancy discrimination (CS+ minus CS-) scores to predict last session GAD-7 scores while controlling for first session GAD-7 score and number of treatment sessions completed.

#### Acquisition
```{r exploratory acq differential}
# Generate model
expl_acq_diff_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_acquisition_differential_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_acq_diff_model)

# Save single row summary of model
expl_acq_diff_model_glance1 <- 
  glance(expl_acq_diff_model)

# Save summary dataframe of test results
expl_acq_diff_model_tidy <- 
  tidy(expl_acq_diff_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - discrimination scores", 
         model = "acquisition differential", 
         .before = everything())
```

#### Extinction
```{r exploratory ext differential}
# Generate model
expl_ext_diff_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_extinction_differential_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_ext_diff_model)

# Save single row summary of model
expl_ext_diff_model_glance1 <- 
  glance(expl_ext_diff_model)

# Save summary dataframe of test results
expl_ext_diff_model_tidy <- 
  tidy(expl_ext_diff_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - discrimination scores", 
         model = "extinction_differential", 
         .before = everything())
```

#### Plot

```{r exploratory differentials combine dataframes}
# Combine tidied dataframes for potential plotting and tables
exploratory_models_tidy1 <-
  rbind(expl_acq_diff_model_tidy, expl_ext_diff_model_tidy) %>%
  mutate(
    sig_05 = if_else(p.value <= 0.05, TRUE, FALSE),
    sig_05_adj = if_else(pval.adj <= 0.05, TRUE, FALSE),
    term = factor(if_else(str_detect(term, "exp_"), "fc", term)),
    iv = case_when(
      term == "gad7_treatment_total_1_z" ~ FALSE,
      term == "ieso_treatment_completed_total_z" ~ FALSE,
      TRUE ~ TRUE
    ),
    term = fct_rev(term)
  )
```

```{r exploratory differentials plot, warning=FALSE}
exploratory_models_tidy1 %>%
  filter(term != "(Intercept)") %>%
  
  # Plot
  forest_plot(data = .,
           x = estimate,
           y = term,
           group = model,
           colour = model,
           alpha = iv,
           point_shape = sig_05_adj,
           error_low = conf.low,
           error_high = conf.high,
           bar_dodge = 0.2,
           x_axis_low = -5, 
           x_axis_high = 5,
           x_axis_break = 1,
           predictor_label_1 = "Acquisition Differential",
           predictor_label_2 = "Extinction Differential") +
  
  # Labels
  scale_y_discrete(
    labels = c(
      "ieso_treatment_completed_total_z" = "Number of treatment sessions",
      "gad7_treatment_total_1_z" = "First session GAD-7 score",
      "fc" = "Fear conditioning predictor"
    )
  ) +
  labs(
    caption = paste0("Intercepts",
      "\nModel 1 = ",
      round(expl_acq_diff_model$coefficients[1], digits = 2),
      "\nModel 2 = ",
      round(expl_ext_diff_model$coefficients[1], digits = 2)
    ))

suppressMessages(ggsave(here("reports", "figures", "exploratory1-regression-forest-plot.png"),
  bg = "white"))
```

### Affective ratings (IV) {.tabset}

The second set of exploratory analyses use affective ratings to predict last session GAD-7 scores while controlling for first session GAD-7 score and number of treatment sessions completed.

#### Post-acquisition CS+
```{r exploratory post-acq cs+}
# Generate model
expl_acq_cs_plus_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      aff_break_cs_plus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_acq_cs_plus_model)

# Save single row summary of model
expl_acq_plus_model_glance2 <- 
  glance(expl_acq_cs_plus_model)

# Save summary dataframe of test results
expl_acq_cs_plus_model_tidy <- 
  tidy(expl_acq_cs_plus_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - affective ratings", 
         model = "post-acquisition cs+", 
         .before = everything())
```

#### Post-acquisition CS-
```{r exploratory post-acq cs-}
# Generate model
expl_acq_cs_minus_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      aff_break_cs_minus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_acq_cs_minus_model)

# Save single row summary of model
expl_acq_minus_model_glance2 <- 
  glance(expl_acq_cs_minus_model)

# Save summary dataframe of test results
expl_acq_cs_minus_model_tidy <- 
  tidy(expl_acq_cs_minus_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - affective ratings", 
         model = "post-acquisition cs-", 
         .before = everything())
```

#### Post-extinction CS+
```{r exploratory post-ext cs+}
# Generate model
expl_ext_cs_plus_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      aff_post_cs_plus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_ext_cs_plus_model)

# Save single row summary of model
expl_ext_plus_model_glance2 <- 
  glance(expl_ext_cs_plus_model)

# Save summary dataframe of test results
expl_ext_cs_plus_model_tidy <- 
  tidy(expl_ext_cs_plus_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - affective ratings", 
         model = "post-extinction cs+", 
         .before = everything())
```

#### Post-extinction CS-
```{r exploratory post-ext cs-}
# Generate model
expl_ext_cs_minus_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      aff_post_cs_minus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_ext_cs_minus_model)

# Save single row summary of model
expl_ext_minus_model_glance2 <- 
  glance(expl_ext_cs_minus_model)

# Save summary dataframe of test results
expl_ext_cs_minus_model_tidy <- 
  tidy(expl_ext_cs_minus_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - affective ratings", 
         model = "post-extinction cs-", 
         .before = everything())
```

#### Plot

```{r exploratory affective ratings combine dataframes}
# Combine tidied dataframes for potential plotting and tables
exploratory_models_tidy2 <-
  rbind(expl_acq_cs_plus_model_tidy, expl_acq_cs_minus_model_tidy,
        expl_ext_cs_plus_model_tidy, expl_ext_cs_minus_model_tidy) %>%
  mutate(
    sig_05 = if_else(p.value <= 0.05, TRUE, FALSE),
    sig_05_adj = if_else(pval.adj <= 0.05, TRUE, FALSE),
    term = factor(if_else(str_detect(term, "aff_"), "fc", term)),
    iv = case_when(
      term == "gad7_treatment_total_1_z" ~ FALSE,
      term == "ieso_treatment_completed_total_z" ~ FALSE,
      TRUE ~ TRUE
    ),
    term = fct_rev(term)
  )
```

```{r exploratory affective ratings plot, warning=FALSE}
exploratory_models_tidy2 %>%
  filter(term != "(Intercept)") %>%
  
  # Plot
  forest_plot(data = .,
           x = estimate,
           y = term,
           group = model,
           colour = model,
           alpha = iv,
           point_shape = sig_05_adj,
           error_low = conf.low,
           error_high = conf.high,
           bar_dodge = 0.4,
           x_axis_low = -10, 
           x_axis_high = 10,
           x_axis_break = 1,
           predictor_label_1 = "Post-acquisition CS+",
           predictor_label_2 = "Post-acquisition CS-",
           predictor_label_3 = "Post-extinction CS+",
           predictor_label_4 = "Post-extinction CS-") +
  
  # Labels
  scale_y_discrete(
    labels = c(
      "ieso_treatment_completed_total_z" = "Number of treatment sessions",
      "gad7_treatment_total_1_z" = "First session GAD-7 score",
      "fc" = "Fear conditioning predictor"
    )
  ) +
  labs(
    caption = paste0("Intercepts",
      "\nModel 1 = ",
      round(expl_acq_cs_plus_model$coefficients[1], digits = 2),
      "\nModel 2 = ",
      round(expl_acq_cs_minus_model$coefficients[1], digits = 2),
      "\nModel 3 = ",
      round(expl_ext_cs_plus_model$coefficients[1], digits = 2),
      "\nModel 4 = ",
      round(expl_ext_cs_minus_model$coefficients[1], digits = 2)
    ))

suppressMessages(ggsave(here("reports", "figures", "exploratory2-regression-forest-plot.png"),
  bg = "white"))
```

### Non-fear conditioning (IVs) {.tabset}

The third set of exploratory analyses uses anxiety-related variables to predict last session GAD-7 scores while controlling for first session GAD-7 score and number of treatment sessions completed.

#### ASI
```{r exploratory asi}
# Generate model
expl_asi_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      asi_baseline_total_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_asi_model)

# Save single row summary of model
expl_asi_model_glance3 <- 
  glance(expl_asi_model)

# Save summary dataframe of test results
expl_asi_model_tidy <- 
  tidy(expl_asi_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - non-fc predictors", 
         model = "asi", 
         .before = everything())
```

#### CBAS
```{r exploratory cbas}
# Generate model
expl_cbas_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      cbas_baseline_total_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_cbas_model)

# Save single row summary of model
expl_cbas_model_glance3 <- 
  glance(expl_cbas_model)

# Save summary dataframe of test results
expl_cbas_model_tidy <- 
  tidy(expl_cbas_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - non-fc predictors", 
         model = "cbas", 
         .before = everything())
```

#### eACS
```{r exploratory eacs}
# Generate model
expl_eacs_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      eacs_midapp_total_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_eacs_model)

# Save single row summary of model
expl_eacs_model_glance3 <- 
  glance(expl_eacs_model)

# Save summary dataframe of test results
expl_eacs_model_tidy <- 
  tidy(expl_eacs_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - non-fc predictors", 
         model = "eacs", 
         .before = everything())
```

#### Plot

```{r exploratory non-fc combine dataframes}
# Combine tidied dataframes for potential plotting and tables
exploratory_models_tidy3 <-
  rbind(expl_asi_model_tidy, expl_cbas_model_tidy, expl_eacs_model_tidy) %>%
  mutate(
    sig_05 = if_else(p.value <= 0.05, TRUE, FALSE),
    sig_05_adj = if_else(pval.adj <= 0.05, TRUE, FALSE),
    term = factor(if_else(str_detect(term, "asi|cbas|eacs"), "predictor", term)),
    iv = case_when(
      term == "gad7_treatment_total_1_z" ~ FALSE,
      term == "ieso_treatment_completed_total_z" ~ FALSE,
      TRUE ~ TRUE
    )
  )

exploratory_models_tidy3
```

```{r exploratory non-fc plot, warning=FALSE}
exploratory_models_tidy3 %>%
  filter(term != "(Intercept)") %>%
  
  # Plot
  forest_plot(data = .,
           x = estimate,
           y = term,
           group = model,
           colour = model,
           alpha = iv,
           point_shape = sig_05_adj,
           error_low = conf.low,
           error_high = conf.high,
           bar_dodge = 0.3,
           x_axis_low = -5, 
           x_axis_high = 5,
           x_axis_break = 1,
           predictor_label_1 = "ASI",
           predictor_label_2 = "CBAS",
           predictor_label_3 = "eACS") +
  
  # Labels
  scale_y_discrete(
    labels = c(
      "ieso_treatment_completed_total_z" = "Number of treatment sessions",
      "gad7_treatment_total_1_z" = "First session GAD-7 score",
      "predictor" = "Predictor"
    )
  ) +
  labs(
    caption = paste0("Intercepts",
      "\nModel 1 = ",
      round(expl_asi_model$coefficients[1], digits = 2),
      "\nModel 2 = ",
      round(expl_cbas_model$coefficients[1], digits = 2),
      "\nModel 3 = ",
      round(expl_eacs_model$coefficients[1], digits = 2)
    ))

suppressMessages(ggsave(here("reports", "figures", "exploratory3-regression-forest-plot.png"),
  bg = "white"))
```

### Depression (covariate) {.tabset}

The fourth set of exploratory analyses repeats the primary analyses while additionally adjusting for depression symptoms.

#### Acquisition CS-

```{r exploratory acq}
# Generate model
expl_acq_minus_dep_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_acquisition_cs_minus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z +
      phq9_treatment_total_1_z,
    data = .
  )

# Model output
summary(expl_acq_minus_dep_model)

# Save single row summary of model
expl_acq_minus_model_glance4 <- 
  glance(expl_acq_minus_dep_model)

# Save summary dataframe of test results
expl_acq_minus_dep_model_tidy <- 
  tidy(expl_acq_minus_dep_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 5)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - depression adjustment", 
         model = "acquisition cs-", 
         .before = everything())
```

#### Extinction CS+

```{r exploratory ext}
# Generate model
expl_ext_plus_dep_model <- 
  port_data_exclusions_applied_std %>%
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_extinction_cs_plus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z +
      phq9_treatment_total_1_z,
    data = .
  )

# Model output
summary(expl_ext_plus_dep_model)

# Save single row summary of model
expl_ext_plus_model_glance4 <- 
  glance(expl_ext_plus_dep_model)

# Save summary dataframe of test results
expl_ext_plus_dep_model_tidy <- 
  tidy(expl_ext_plus_dep_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 5)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - depression adjustment", 
         model = "extinction cs+", 
         .before = everything())
```

#### Plot

```{r exploratory depression control combine dataframes}
# Combine tidied dataframes for potential plotting and tables
exploratory_models_tidy4 <-
  rbind(expl_acq_minus_dep_model_tidy, expl_ext_plus_dep_model_tidy) %>%
  mutate(
    sig_05 = if_else(p.value <= 0.05, TRUE, FALSE),
    sig_05_adj = if_else(pval.adj <= 0.05, TRUE, FALSE),
    term = factor(if_else(str_detect(term, "exp_"), "fc", term)),
    iv = case_when(
      term == "gad7_treatment_total_1_z" ~ FALSE,
      term == "ieso_treatment_completed_total_z" ~ FALSE,
      term == "phq9_treatment_total_1_z" ~ FALSE,
    ),
    term = factor(
      term,
      level = c(
        "(Intercept)",
        "ieso_treatment_completed_total_z",
        "gad7_treatment_total_1_z",
        "phq9_treatment_total_1_z",
        "fc"
      )
    )
  )
```

```{r exploratory depression control plot, warning=FALSE}
exploratory_models_tidy4 %>%
  filter(term != "(Intercept)") %>%
  
  # Plot
  forest_plot(data = .,
           x = estimate,
           y = term,
           group = model,
           colour = model,
           alpha = iv,
           point_shape = sig_05_adj,
           error_low = conf.low,
           error_high = conf.high,
           bar_dodge = 0.2,
           x_axis_low = -5, 
           x_axis_high = 5,
           x_axis_break = 1) +
  
  # Labels
  scale_y_discrete(
    labels = c(
      "ieso_treatment_completed_total_z" = "Number of treatment sessions",
      "gad7_treatment_total_1_z" = "First session GAD-7 score",
      "phq9_treatment_total_1_z" = "First session PHQ-9 score",
      "fc" = "Fear conditioning predictor"
    )
  ) +
  labs(
    caption = paste0("Intercepts",
      "\nModel 1 = ",
      round(expl_acq_minus_dep_model$coefficients[1], digits = 2),
      "\nModel 2 = ",
      round(expl_ext_plus_dep_model$coefficients[1], digits = 2)
    )
  )

suppressMessages(ggsave(here("reports", "figures", "exploratory4-regression-forest-plot.png"),
  bg = "white"))
```

### Low GAD-7 excluded {.tabset}

The fifth set of exploratory analyses repeats those from the primary analyses with participants excluded if their GAD-7 score is lower than eight on their first treatment session.

#### Acquisition CS-

```{r exploratory low gad exclusion acq}
# Generate model
expl_acq_low_anx_exc_model <- 
  port_data_exclusions_applied_std %>%
  filter(gad7_treatment_total_1 >= 8) %>% 
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_acquisition_cs_minus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_acq_low_anx_exc_model)

# Save single row summary of model
expl_acq_minus_model_glance5 <- 
  glance(expl_acq_low_anx_exc_model)

# Save summary dataframe of test results
expl_acq_low_anx_exc_model_tidy <- 
  tidy(expl_acq_low_anx_exc_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - low gad excluded", 
         model = "acquisition cs-", 
         .before = everything())
```

#### Extinction CS+

```{r exploratory low gad exclusion ext}
# Generate model
expl_ext_low_anx_exc_model <- 
  port_data_exclusions_applied_std %>%
  filter(gad7_treatment_total_1 >= 8) %>% 
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_extinction_cs_plus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_ext_low_anx_exc_model)

# Save single row summary of model
expl_ext_plus_model_glance5 <- 
  glance(expl_ext_low_anx_exc_model)

# Save summary dataframe of test results
expl_ext_low_anx_exc_model_tidy <- 
  tidy(expl_ext_low_anx_exc_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - low gad excluded", 
         model = "extinction cs+", 
         .before = everything())
```

#### Plot

```{r exploratory low gad exclusion combine dataframes}
# Combine tidied dataframes for potential plotting and tables
exploratory_models_tidy5 <-
  rbind(expl_acq_low_anx_exc_model_tidy, expl_ext_low_anx_exc_model_tidy) %>%
  mutate(
    sig_05 = if_else(p.value <= 0.05, TRUE, FALSE),
    sig_05_adj = if_else(pval.adj <= 0.05, TRUE, FALSE),
    term = factor(if_else(str_detect(term, "exp_"), "fc", term)),
    iv = case_when(
      term == "gad7_treatment_total_1_z" ~ FALSE,
      term == "ieso_treatment_completed_total_z" ~ FALSE,
      TRUE ~ TRUE
    ),
    term = fct_rev(term)
  )
```

```{r exploratory low gad exclusion plot, warning=FALSE}
exploratory_models_tidy5 %>%
  filter(term != "(Intercept)") %>%
  
  # Plot
  forest_plot(data = .,
           x = estimate,
           y = term,
           group = model,
           colour = model,
           alpha = iv,
           point_shape = sig_05_adj,
           error_low = conf.low,
           error_high = conf.high,
           bar_dodge = 0.2,
           x_axis_low = -5, 
           x_axis_high = 5,
           x_axis_break = 1) +
  
  # Labels
  scale_y_discrete(
    labels = c(
      "ieso_treatment_completed_total_z" = "Number of treatment sessions",
      "gad7_treatment_total_1_z" = "First session GAD-7 score",
      "fc" = "Fear conditioning predictor"
    )
  ) + 
  labs(
    caption = paste0("Intercepts",
      "\nModel 1 = ",
      round(expl_acq_low_anx_exc_model$coefficients[1], digits = 2),
      "\nModel 2 = ",
      round(expl_ext_low_anx_exc_model$coefficients[1], digits = 2)
    ))

suppressMessages(ggsave(here("reports", "figures", "exploratory5-regression-forest-plot.png"),
       bg = "white"))
```

### Non-completers excluded {.tabset}

The sixth set of exploratory analyses repeats those from the primary analyses with participants excluded if they were not classified as treatment completers.

#### Acquisition CS-

```{r exploratory treatment completers acq}
# Generate model
expl_acq_treat_complete_model <- 
  port_data_exclusions_applied_std %>%
  filter(ieso_discharge_reason_primary == "completed_treatment") %>% 
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_acquisition_cs_minus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_acq_treat_complete_model)

# Save single row summary of model
expl_acq_minus_model_glance6 <- 
  glance(expl_acq_treat_complete_model)

# Save summary dataframe of test results
expl_acq_treat_complete_model_tidy <- 
  tidy(expl_acq_treat_complete_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - treatment completers", 
         model = "acquisition cs-", 
         .before = everything())
```

#### Extinction CS+

```{r exploratory treatment completers ext}
# Generate model
expl_ext_treat_complete_model <- 
  port_data_exclusions_applied_std %>%
  filter(ieso_discharge_reason_primary == "completed_treatment") %>% 
  lm(
    gad7_treatment_total_final_observed ~ 
      exp_extinction_cs_plus_mean_z + 
      gad7_treatment_total_1_z + 
      ieso_treatment_completed_total_z,
    data = .
  )

# Model output
summary(expl_ext_treat_complete_model)

# Save single row summary of model
expl_ext_plus_model_glance6 <- 
  glance(expl_ext_treat_complete_model)

# Save summary dataframe of test results
expl_ext_treat_complete_model_tidy <- 
  tidy(expl_ext_treat_complete_model, conf.int = T) %>% 
  # Add column of adjusted p-values (holm correction)
  mutate(pval.adj = p.adjust(p.value, method = "holm", n = 4)) %>% 
  # Add column describing model for later merge
  mutate(analysis = "exploratory - treatment completers", 
         model = "extinction cs+", 
         .before = everything())
```

#### Plot

```{r exploratory treatment completers combine dataframes}
# Combine tidied dataframes for potential plotting and tables
exploratory_models_tidy6 <-
  rbind(expl_acq_treat_complete_model_tidy, expl_ext_treat_complete_model_tidy) %>%
  mutate(
    sig_05 = if_else(p.value <= 0.05, TRUE, FALSE),
    sig_05_adj = if_else(pval.adj <= 0.05, TRUE, FALSE),
    term = factor(if_else(str_detect(term, "exp_"), "fc", term)),
    iv = case_when(
      term == "gad7_treatment_total_1_z" ~ FALSE,
      term == "ieso_treatment_completed_total_z" ~ FALSE,
      TRUE ~ TRUE
    ),
    term = fct_rev(term)
  )
```

```{r exploratory treatment completers plot, warning=FALSE}
exploratory_models_tidy6 %>%
  filter(term != "(Intercept)") %>%
  
  # Plot
  forest_plot(data = .,
           x = estimate,
           y = term,
           group = model,
           colour = model,
           alpha = iv,
           point_shape = sig_05_adj,
           error_low = conf.low,
           error_high = conf.high,
           bar_dodge = 0.2,
           x_axis_low = -5, 
           x_axis_high = 5,
           x_axis_break = 1) +
  
  # Labels
  scale_y_discrete(
    labels = c(
      "ieso_treatment_completed_total_z" = "Number of treatment sessions",
      "gad7_treatment_total_1_z" = "First session GAD-7 score",
      "fc" = "Fear conditioning predictor"
    )
  ) + 
  labs(
    caption = paste0("Intercepts",
      "\nModel 1 = ",
      round(expl_acq_treat_complete_model$coefficients[1], digits = 2),
      "\nModel 2 = ",
      round(expl_ext_treat_complete_model$coefficients[1], digits = 2)
    ))

suppressMessages(ggsave(here("reports", "figures", "exploratory6-regression-forest-plot.png"),
       bg = "white"))
```

```{r save regression tables}
regression_model_coefficients <- rbind(
  primary_models_tidy,
  secondary_models_tidy1,
  secondary_models_tidy2,
  secondary_models_tidy3,
  exploratory_models_tidy1,
  exploratory_models_tidy2,
  exploratory_models_tidy3,
  exploratory_models_tidy4,
  exploratory_models_tidy5,
  exploratory_models_tidy6
)

regression_model_fits <- rbind(
  pri_acq_minus_model_glance,
  pri_ext_plus_model_glance,
  sec_acq_minus_model_glance1,
  sec_ext_plus_model_glance1,
  sec_acq_minus_model_glance2,
  sec_ext_plus_model_glance2,
  sec_acq_minus_model_glance3,
  sec_ext_plus_model_glance3,
  expl_acq_diff_model_glance1, 
  expl_ext_diff_model_glance1, 
  expl_acq_plus_model_glance2, 
  expl_acq_minus_model_glance2, 
  expl_ext_plus_model_glance2, 
  expl_ext_minus_model_glance2, 
  expl_asi_model_glance3, 
  expl_cbas_model_glance3, 
  expl_eacs_model_glance3, 
  expl_acq_minus_model_glance4, 
  expl_ext_plus_model_glance4, 
  expl_acq_minus_model_glance5, 
  expl_ext_plus_model_glance5, 
  expl_acq_minus_model_glance6, 
  expl_ext_plus_model_glance6
) %>%
  mutate(
    analysis = c(
      "primary",
      "primary",
      "secondary - age and sex adjustment",
      "secondary - age and sex adjustment",
      "secondary - gad7 followup dv",
      "secondary - gad7 followup dv",
      "secondary - fss followup dv",
      "secondary - fss followup dv",
      "exploratory - discrimination scores",
      "exploratory - discrimination scores",
      "exploratory - affective ratings",
      "exploratory - affective ratings",
      "exploratory - affective ratings",
      "exploratory - affective ratings",
      "exploratory - non-fc predictors",
      "exploratory - non-fc predictors",
      "exploratory - non-fc predictors",
      "exploratory - depression adjustment", 
      "exploratory - depression adjustment", 
      "exploratory - low gad excluded",
      "exploratory - low gad excluded",
      "exploratory - treatment completers",
      "exploratory - treatment completers"
    ),
    model = c(
      "acquisition_cs_minus",
      "extinction_cs_plus",
      "acquisition_cs_minus",
      "extinction_cs_plus",
      "acquisition_cs_minus",
      "extinction_cs_plus",
      "acquisition_cs_minus",
      "extinction_cs_plus",
      "acquisition",
      "exctinction",
      "post-acquisition_cs_plus",
      "post-acquisition_cs_minus",
      "post-extinction_cs_plus",
      "post-extinction_cs_minus",
      "asi",
      "cbas",
      "eacs",
      "acquisition_cs_minus",
      "extinction_cs_plus",
      "acquisition_cs_minus",
      "extinction_cs_plus",
      "acquisition_cs_minus",
      "extinction_cs_plus"
    ),
    .before = everything()
  )

write_csv(
  regression_model_coefficients,
  here("reports", "tables", "regression_model_coefficients.csv")
)
write_csv(regression_model_fits,
          here("reports", "tables", "regression_model_fits.csv"))
```

## Not pre-registered {.tabset}

### Percentage of extinction learning
Mean CR [(CS+) - (CS-)] of early extinction learning - mean CR [(CS+) - (CS-)] of last two trials of conditioning
```{r}
test <- port_data_exclusions_applied_std %>%
  mutate(
    exp_extinction_cs_plus_1_to_6_mean =
      rowMeans(
        select(
          .,
          exp_extinction_cs_plus_1,
          exp_extinction_cs_plus_2,
          exp_extinction_cs_plus_3,
          exp_extinction_cs_plus_4,
          exp_extinction_cs_plus_5,
          exp_extinction_cs_plus_6
        )
      ),
    exp_extinction_cs_minus_1_to_6_mean =
      rowMeans(
        select(
          .,
          exp_extinction_cs_minus_1,
          exp_extinction_cs_minus_2,
          exp_extinction_cs_minus_3,
          exp_extinction_cs_minus_4,
          exp_extinction_cs_minus_5,
          exp_extinction_cs_minus_6
        )
      ),
    exp_acquisition_cs_plus_11_to_12_mean =
      rowMeans(
        select(.,
               exp_acquisition_cs_plus_11,
               exp_acquisition_cs_plus_12)
      ),
    exp_acquisition_cs_minus_11_to_12_mean =
      rowMeans(
        select(.,
               exp_acquisition_cs_minus_11,
               exp_acquisition_cs_minus_12)
      ),
    exp_extinction_1_to_6_difference_in_means = exp_extinction_cs_plus_1_to_6_mean - exp_extinction_cs_minus_1_to_6_mean,
    exp_acquisition_11_to_12_difference_in_means = exp_acquisition_cs_plus_11_to_12_mean - exp_acquisition_cs_minus_11_to_12_mean,
    proportion_extinction_1_to_6_acquisition_11_to_12_difference_in_means = exp_extinction_1_to_6_difference_in_means / exp_acquisition_11_to_12_difference_in_means
  )

summary(test$proportion_extinction_1_to_6_acquisition_11_to_12_difference_in_means)
glimpse(test)
```


### Anxiety diagnoses only

### Exposure treatment only

# Visualisations {.tabset}

## Elephant

```{r elephant wrangling, include=FALSE}
# Create a list of expectancy rating trial variables
elephant_long <- port_data_exclusions_applied %>% 
  select(matches("^exp_.*\\d$")) %>%
  mutate(n = nrow(.)) %>% 
  pivot_longer(cols = -n, names_to = "variable", values_to = "rating") %>% 
  mutate(variable = str_remove(variable, "exp_")) %>%
  separate(variable, into = c("phase", "cs", "stimulus", "trial"), sep = "_") %>% 
  select(-cs) %>% 
  mutate(trial = as.numeric(trial)) %>% 
  group_by(phase, stimulus, trial) %>% 
  summarise(mean = mean(rating, na.rm = T), std_dev = sd(rating, na.rm = T), n = mean(n), .groups = "keep") %>% 
  mutate(sem = std_dev / sqrt(n),
         ci_low = mean - 2*(sem),
         ci_high = mean + 2*(sem)) %>% 
  ungroup() %>% 
  mutate(Phase = str_to_sentence(phase),
         Phase = factor(Phase, levels = c("Acquisition", "Extinction")),
         Stimulus = factor(stimulus, levels = c("plus", "minus")),
         Stimulus = fct_recode(Stimulus, "CS+" = "plus", "CS-" = "minus")) %>% 
  select(Phase, Stimulus, Trial = trial, everything()) %>% 
  select(-c(phase, stimulus)) %>% 
  arrange(Phase, Stimulus, Trial)

# Function for breaks
breaks_fun <- function(x) {
  if (max(x) > 12) {
    seq(0, 18, 1)
  } else {
    seq(0, 12, 1)
  }
}
```

```{r elephant plot}
elephant_plot_exclusions_applied <- elephant_long %>% 
  ggplot(aes(x = Trial, y = mean, color = Stimulus)) +
  geom_point() +
  geom_line() +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high, fill = Stimulus),
              linetype = 0,
              alpha = 0.3,
              linewidth = 0.8
  ) +
  scale_fill_manual(values = c("#811D1C", "#153860")) +
  scale_colour_manual(values = c("#811D1C", "#153860")) +
  facet_grid(~ Phase, 
               scales = "free_x",
               space = "free_x"
    ) +
    # adjust the labels
    labs(y="Mean expectancy rating", 
         x = "Trials"
    ) +
    theme(strip.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = 'bottom',
          text = element_text(size = 10),
          strip.text.x = element_text(size = 10)
    ) +
    scale_x_continuous(breaks = breaks_fun) +
    scale_y_continuous(breaks = seq(0, 10, by = 1), limits = c(1, 9))

elephant_plot_exclusions_applied

# Save
ggsave(
  file = paste0(here("reports", "figures"), "/elephant-plot_exclusions-applied.png"), 
  plot = elephant_plot_exclusions_applied, 
  width = 16, 
  height = 8, 
  units = "cm",
  bg = "white"
  )
```
